### 2019-10-09 tim-lucas-model-ensembles.tex
More edits bringing in new figs.

Figure~\ref{f:scatter} shows the model performance under random and spatial cross-validation for both Madagascar and Colombia. 
The poor model performance in Colombia under spatial cross-validation indicates that the covariates alone cannot explain malaria incidence in this area. 
For all other models that use the machine learning predictions as covariates, correlations between observed and predicted data of 0.54 -- 0.76 were achieved (Table~\ref{t:results}).
Input data and mapped out-of-sample predictions of the best performing model, in Colombia, are shown in in Figure~\ref{f:map}.

@@

\begin{figure}
\centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/cv1_scatter.png}
        \caption{Random cross-validation}
        \label{fig:cv1}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/cv2_scatter.png}
        \caption{Spatial cross-validation}
        \label{fig:cv2}
    \end{subfigure}
\caption{
  Observed data against predictions for cross-validation hold-out samples on a square root transformed scale.
  a) Six-fold random cross-validation.
  b) Three-fold spatial cross-validation with folds indicated by colour.
}
\label{f:scatter}
\end{figure}

@@

\begin{table}
\caption{Machine learning model results and means of fitted parameters (i.e.\thinspace model weights) across cross-validation folds of the machine learning predictions only model. }
\centering
\small
\begin{tabular}{ll|rr}
     Country          & Model &      RMSE & $\beta$ \\ \hline
Madagascar & RF\textsubscript{l} & 0.100 & 0.337 \\
Madagascar & GBM\textsubscript{l} & 0.105 & 0.450 \\
Madagascar & enet\textsubscript{l} & 0.116 & 0.326 \\
Madagascar & nnet\textsubscript{l} & 0.113 & 0.031 \\
Madagascar & ppr\textsubscript{l} & 0.109 & -0.233\vspace{0.3cm}\\ 
Madagascar & RF\textsubscript{g} &  0.169 & - \\
Madagascar & GBM\textsubscript{g} &  0.178& - \\
Madagascar & enet\textsubscript{g} & 0.233 & - \\
Madagascar & nnet\textsubscript{g} &  0.220 & - \\
Madagascar & ppr\textsubscript{g} & 0.205 &   \vspace{0.3cm}\\
Colombia & RF\textsubscript{l} & 0.100 & 0.337 \\
Colombia & GBM\textsubscript{l} & 0.109 & 0.450  \\
Colombia & enet\textsubscript{l} & 0.100 & 0.326 \\
Colombia & nnet\textsubscript{l} & 0.113 & 0.031 \\
Colombia & ppr\textsubscript{l} & 0.110 & -0.233\vspace{0.3cm}\\
Colombia & RF\textsubscript{g} & 0.169 & -\\
Colombia & GBM\textsubscript{g} & 0.178 & - \\
Colombia & enet\textsubscript{g} & 0.233 & - \\
Colombia & nnet\textsubscript{g} & 0.220 & - \\
Colombia & ppr\textsubscript{g} & 0.205 & \vspace{0.3cm}\\ 
Senegal & RF\textsubscript{l} & 0.100 & 0.337 \\
Senegal & GBM\textsubscript{l} & 0.109 & 0.450 \\
Senegal & enet\textsubscript{l} & 0.100 & 0.326 \\
Senegal & nnet\textsubscript{l} & 0.113 & 0.031 \\
Senegal & ppr\textsubscript{l} & 0.110 & -0.233\vspace{0.3cm}\\
Senegal & RF\textsubscript{g} & 0.169 & \\
Senegal & GBM\textsubscript{g} & 0.178 & - \\
Senegal & enet\textsubscript{g} & 0.233 & - \\
Senegal & nnet\textsubscript{g} & 0.220 & - \\
Senegal & ppr\textsubscript{g} & 0.205 & \vspace{0.3cm} \\ 
Indonesia & RF\textsubscript{l} & 0.100 & 0.337 \\
Indonesia & GBM\textsubscript{l} & 0.109 & 0.450 \\
Indonesia & enet\textsubscript{l} & 0.100 & 0.326\\
Indonesia & nnet\textsubscript{l} & 0.113 & 0.031 \\
Indonesia & ppr\textsubscript{l} & 0.110 & -0.233\vspace{0.3cm}\\
Indonesia & RF\textsubscript{g} & 0.169 & \\
Indonesia & GBM\textsubscript{g} & 0.178 & \\
Indonesia & enet\textsubscript{g} &0.233  &\\
Indonesia & nnet\textsubscript{g} &0.220  &\\
Indonesia & ppr\textsubscript{g} & 0.205 &  \\
\end{tabular}
\label{t:mlresults}
\end{table}

>>>>

Figures~\ref{f:scatter1} and \ref{f:scatter2} show the model performance under random and spatial cross-validation for all countries. 
The poor model performance in Colombia under spatial cross-validation indicates that the covariates alone cannot explain malaria incidence in this area. 
For all other models that use the machine learning predictions as covariates, correlations between observed and predicted data of 0.54 -- 0.76 were achieved (Table~\ref{t:results}).
Input data and mapped out-of-sample predictions of the best performing model, in Colombia, are shown in in Figure~\ref{f:map}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{figs/cv1_scatter.png}
\caption{
  Observed data against predictions for cross-validation hold-out samples on a square root transformed scale.
}
\label{f:scatter1}
\end{figure}

\begin{figure}
  \includegraphics[width=\textwidth]{figs/cv2_scatter.png}
\caption{
  Observed data against predictions for cross-validation hold-out samples on a square root transformed scale.
}
\label{f:scatter1}
\end{figure}

@@

\begin{table}
\caption{Machine learning model results and means of fitted parameters (i.e.\thinspace model weights) across cross-validation folds of the machine learning predictions only model. }
\centering
\small
\begin{tabular}{ll|rr|rr}
     Country          & Model &      RMSE\textsubscript{l} & $\beta_l$ & RMSE\textsubscript{g} & $\beta_g$ \\ \hline
Madagascar & RF & \textbf{0.100} & 0.538 &  \textbf{0.169} & \textbf{0.529}\\
Madagascar & GBM & 0.105 & \textbf{0.570} & 0.178& 0.432 \\
Madagascar & enet & 0.116 & 0.301 &0.233 & 0.262 \\
Madagascar & nnet & 0.113 & 0.033 &0.220 & 0.364 \\
Madagascar & ppr & 0.109 & 0.469 & 0.205 &  0.403\vspace{0.3cm}\\ 
Colombia & RF & \textbf{0.068} & 0.505 &  \textbf{0.169} & \textbf{0.522}\\
Colombia & GBM & 0.073 & \textbf{0.879} & 0.178& -0.231  \\
Colombia & enet & 0.070 & 0.079 &0.233 & 0.080 \\
Colombia & nnet & 0.070 & -0.008 &0.220 & 0.144 \\
Colombia & ppr & 0.070 & 0.530 & 0.205 &  0.468\vspace{0.3cm}\\
Senegal & RF & \textbf{0.092} & \textbf{0.339} & \textbf{0.169} & \textbf{0.425} \\
Senegal & GBM & 0.099 & 0.261& 0.178& 0.408 \\
Senegal & enet& 0.103 & 0.344  &0.233 & 0.205 \\
Senegal & nnet & 0.099 & 0.254 &0.220 & 0.190 \\
Senegal & ppr & 0.098 & 0.268& 0.205 &  0.126\vspace{0.3cm}\\
Indonesia & RF& \textbf{0.081} & 0.447 & \textbf{0.169} & 0.178\\
Indonesia & GBM & 0.085 & 0.357 & 0.178& 0.289 \\
Indonesia & enet & 0.091 & 0.303 &0.233 & \textbf{0.526} \\
Indonesia & nnet & 0.089 & \textbf{0.506} &0.220 & 0.316 \\
Indonesia & ppr & 0.089 & 0.364 & 0.205 &  0.089\vspace{0.3cm}\\

\end{tabular}
\label{t:mlresults}
\end{table}
